Descriptive analysis

### 2020-03-08 analysis/02_descriptive-analysis.Rmd
Turn off warnings

```{r model-pts-restrictions, cache=TRUE, message=FALSE, results="hide"}
diff_ngo_pts <- brm(
  bf(barriers_total ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
  family = student,
  data = select(canary, barriers_total, PTS_factor),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_ngo_pts")
)
```

>>>>

```{r model-pts-restrictions, cache=TRUE, message=FALSE, warning=FALSE, results="hide"}
diff_ngo_pts <- brm(
  bf(barriers_total ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
  family = student,
  data = select(canary, barriers_total, PTS_factor),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_ngo_pts")
)
```
